### 2015-10-15 thesis-proposal/problem.tex
Updated link to thesis repo
fixed typo
fixed?

\section{Typed Syntax Macros (TSMs)}\label{sec:tsms}
We will now introduce a new external primitive -- the \textbf{typed syntax macro} (TSM) -- that combines the syntactic flexibility of syntax extensions with the reasoning guarantees of typed macros. Like the term-rewriting macros just described, TSMs can be parameterized by modules, so they can be used to define syntax valid at any abstract type defined by a module satisfying a specified signature. As we will discuss in the remainder of this section, this addresses all of the problems brought up above, at moderate syntactic cost.

\subsection{TSMs by Example}\label{sec:tsms-by-example}
%A typed syntax macro is invoked by applying it to a \emph{delimited form}, which can contain  arbitrary syntax in its \emph{body}.  
To introduce TSMs, consider the following concrete external expression:
\begin{lstlisting}[numbers=none]
rx P /SURLA|T|G|CEURL/
\end{lstlisting}
Here, we apply a \emph{parameterized TSM}, \lstinline{rx}, first to a module parameter, \lstinline{R}, then to a \emph{delimited form}, \lstinline{/SURLA|T|G|CEURL/}. A number of alternative delimiters are also available in Verse's concrete syntax and could equivalently have been used, e.g. \lstinline{<SURLA|T|G|CEURL>}. The TSM statically parses the \emph{body} of the provided delimited form, i.e. the characters between the delimiters (indicated here in blue), and computes an \emph{expansion}, i.e. another expression. In this case, \lstinline{pattern} generates the following expansion (written concretely):

@@

\url{https://github.com/cyrus-/papers/blob/master/thesis/omar-thesis.pdf}
%To validate our claims of expressiveness, I plan to give several more examples drawn from existing languages. I will include those we have worked out in the papers just cited as well as additional examples that highlight the benefits of integration with Verse's ML-based module system. %For example, I will discuss implementing Haskell's primitive ``do'' syntax using TSLs together with a modular encoding of monads (as described on Prof. Harper's blog \cite{SML/Monads}). I will also show how parser generators and quasiquotation (e.g. as in Scala \cite{shabalin2013quasiquotes} or Lisp \cite{Bawd99a}) can be seen as modes of use of TSMs/TSLs. 
%I will also briefly summarize the corpus analysis we conducted in \cite{TSLs} where we found a large number of  situations in large publicly available Java libraries where dynamic string parsing was apparently being used to control syntactic cost. I anticipate that writing these examples will take an additional 1 week of work, which I will do after finishing the technical work above. %bringing the total for this portion of the dissertation up to about 5 weeks of writing (plus time for review by the committee). %Adding in the time I will need to propose and some buffer time for unanticipated issues, my goal is to have this portion of the dissertation complete by the end of Summer 2015.

>>>>

\section{Typed Syntax Macros (TSMs)}\label{sec:tsms}
We will now introduce a new primitive -- the \textbf{typed syntax macro} (TSM) -- that combines the syntactic flexibility of syntax extensions with the reasoning guarantees of typed macros. Like the term-rewriting macros just described, TSMs can be parameterized by modules, so they can be used to define syntax valid at any abstract type defined by a module satisfying a specified signature. As we will discuss in the remainder of this section, this addresses all of the problems brought up above, at moderate syntactic cost.

\subsection{TSMs By Example}\label{sec:tsms-by-example}
%A typed syntax macro is invoked by applying it to a \emph{delimited form}, which can contain  arbitrary syntax in its \emph{body}.  
To introduce TSMs, consider the following concrete external expression:
\begin{lstlisting}[numbers=none]
rx P /SURLA|T|G|CEURL/
\end{lstlisting}
Here, we apply a \emph{parameterized TSM}, \lstinline{rx}, first to a module parameter, \lstinline{R}, then to a \emph{delimited form}, \lstinline{/SURLA|T|G|CEURL/}. A number of alternative delimiters are also available in Verse's concrete syntax and could equivalently have been used, e.g. \lstinline{<SURLA|T|G|CEURL>}. The TSM statically parses the \emph{body} of the provided delimited form, i.e. the characters between the delimiters (indicated here in blue), and computes an \emph{expansion}, i.e. another expression. In this case, \lstinline{pattern} generates the following expansion (written concretely):

@@

\url{https://github.com/cyrus-/thesis/blob/master/omar-thesis.pdf}
%To validate our claims of expressiveness, I plan to give several more examples drawn from existing languages. I will include those we have worked out in the papers just cited as well as additional examples that highlight the benefits of integration with Verse's ML-based module system. %For example, I will discuss implementing Haskell's primitive ``do'' syntax using TSLs together with a modular encoding of monads (as described on Prof. Harper's blog \cite{SML/Monads}). I will also show how parser generators and quasiquotation (e.g. as in Scala \cite{shabalin2013quasiquotes} or Lisp \cite{Bawd99a}) can be seen as modes of use of TSMs/TSLs. 
%I will also briefly summarize the corpus analysis we conducted in \cite{TSLs} where we found a large number of  situations in large publicly available Java libraries where dynamic string parsing was apparently being used to control syntactic cost. I anticipate that writing these examples will take an additional 1 week of work, which I will do after finishing the technical work above. %bringing the total for this portion of the dissertation up to about 5 weeks of writing (plus time for review by the committee). %Adding in the time I will need to propose and some buffer time for unanticipated issues, my goal is to have this portion of the dissertation complete by the end of Summer 2015.
